\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{fancy} % style options are 'casual' (default), 'classic', 'oldstyle', 'banking', 'fancy'
\moderncvcolor{blue}    % color options are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'

% adjust the pager margins
\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{1.5in}

% personal data
\name{Edimar Calebe}{Castanho}
\title{Software Developer}
\email{contato@calebe.dev.br}
\phone[mobile]{+55~(41)~99827~1302}
\social[linkedin]{calebe94}
\social[github]{calebe94}
\extrainfo{\faRss\href{https://blog.calebe.dev.br/}{blog.calebe.dev.br}}
\begin{document}

\maketitle
% \makecvtitle

\section{Summary}
\cvitem{}{Highly motivated software developer with 3 years of experience developing web applications using JavaScript, React, and Node.js. Seeking a challenging role in a dynamic organization where I can utilize my skills and knowledge to contribute to the success of the company.}

\section{Education}
\cventry{2016--2021}{Bachelor of Computer Engineering}{University of California, Berkeley}{Berkeley, CA}{}{}

\section{Technical Skills}
\cvitem{Programming Languages}{JavaScript, HTML, CSS, Python}
\cvitem{Frameworks}{React, Node.js, Express.js}
\cvitem{Tools}{Git, VS Code, Jira}

\section{Work Experience}
\cventry{2021--Present}{Software Developer}{ABC Company}{San Francisco, CA}{}{Developed and maintained web applications using JavaScript, React, and Node.js. Collaborated with cross-functional teams to deliver projects on time and within budget. Improved application performance by implementing best practices and optimizing code.}

\cventry{2020--2021}{Intern Software Developer}{XYZ Company}{San Jose, CA}{}{Developed web applications using React and Node.js. Worked closely with senior developers to learn and improve coding skills.}

\section{Projects}
\cvitem{E-commerce Website}{Developed an e-commerce website using React, Node.js, and MongoDB. Implemented user authentication and payment gateway integration.}

\cvitem{Weather App}{Built a weather app using React and the OpenWeather API. Implemented geolocation and real-time weather updates.}

\section{Certifications}
\cvitem{AWS Certified Developer - Associate}{Amazon Web Services}

\section{Awards and Recognition}
\cvitem{Employee of the Month}{ABC Company}

\section{References}
\cvitem{}{Available upon request}

\end{document}
